Evolution of Processes in Delivering Reliable Software in the European Scientific Arena

### 2018-06-15 paper-ieee-trans.tex
better link last sentence
fix

Lessons learned show that sustainability is a key pursuit. The achievements, in terms of
processes, knowledge, software and infrastructures, shall be profited from former successful 
completed projects. In this regard, the more recent project described in this paper, {\sl INDIGO-DataCloud},
may have set the path for future reference in the European software development research ecosystem.
The SQA criteria, describing the quality requirements that might be considered during the entire
software lifecycle, have been published as open access and it is periodically reviewed to incorporate
new recommendations and best practices. Successful software products created during the lifetime of the 
project are maintained leveraging the same source code repositories and CI infrastructure. Seamless 
knowledge transfer among software development initiatives is key for the good progress of delivering
reliable software.

>>>>

Lessons learned show that sustainability is a key pursuit. The achievements, in terms of
processes, knowledge, software and infrastructures, shall be profited from former successful 
completed projects. In this regard, the more recent project described in this paper, {\sl INDIGO-DataCloud},
may have set the path for future reference in the European software development research ecosystem.
The SQA criteria, describing the quality requirements that might be considered during the entire
software lifecycle, have been published as open access and periodically reviewed to incorporate
new recommendations and best practices. Successful software products created during the lifetime of the 
project are maintained leveraging the same source code repositories and CI infrastructure. A seamless 
knowledge transfer among subsequent software development initiatives is key for the good progress of
delivering reliable software.
